---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)

library(tidyverse)
library(classdata)

data(ames, package = "classdata")
```

# Lab 02 Report

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.


# Step 1 result
```{r}
ames |> slice_head(n = 6)
dim(ames)
```
```{r}
glimpse(ames)
```

```{r}
summary(ames)
```

**Samara's thoughts:** The variables included are ParcelID, Address, Style, Occupancy, Sale Date, Sale Price, Multi Sale, YearBuilt, Acres, TotalLivingArea(sf), Bedrooms, FinishedBsmtArea(sf), LotArea(sf), AC, FirePlace, and Neighborhood. Here is a list of the types, meanings, and data range for each of the variables:
- ParcelID(String), just a character with ID
- Address(String), property address in Ames, IA
- Style (Factor variable), detailing the type of housing. Most popular ones are "1 Story Frame", "2 Story Frame", and "1 1/2 Story Frame"
- Occupancy (Factory variable), type of housing. Most popular ones are "Condominium", "Single-Family", and "Townhouse".
- Sale Date (Date), date of sale, ranging from 2017-07-03 to 2022-08-31
- Sale Price (Number), is the price of sale (in US dollar), ranging from 0 to 20,500,000
- Multi Sale (String), was this sale part of a package?
- YearBuild (Number), year in which the house was built, ranging from 0 to 2022
- Acres (Number), acres of the lot, ranging from 0 to 12.012
- TotalLivingArea (Number), total living area in sf, ranging from 0 to 6007
- Bedrooms (Number), number of bedrooms, ranging from 0 to 10
- FinishedBsmtArea(Number), total area of the finished basement in sf, ranging from 10 to 6496
- LotArea (Number), total area of the lot in sf, ranging from 0 to 523,228
- AC (String), logical value of if the property has AC or not
- FirePlace (String), logical balue of if the property has a FirePlace or not
- Neighborhood (Factor), factor variable of a level that indicates the neighboorhood area in Ames. Popular ones are "N Ames", "College Creek", and "Investor Owned."

**Wyatt's thoughts:** The data set contains 6935 rows and 16 columns, where rows represent a residential property sale. Key variables include year built, acres, neighborhood, and TotalLivingArea. The main variable is Sale Price which represents the final sale price of the home. Depending on the variables listed above cna chang the range of the variables.

**Tanisha's thoughts:** The dataset contains 6,935 rows and 16 columns, where each row represents a residential property sale. Some main variables include Year Built, Neighborhood, and Total Living Area, while the main variable is Sale Price, which shows the final selling price of the home its value can change based on other variables in the dataset.

**(Combined) As a team, we found that** the dataset provides detailed information about residential property sales in Ames, Iowa. Each of the 6,935 rows represents a single property sale, while the 16 columns describe different characteristics of the property such as its location, size, structure, and sale details. Important variables include Sale Price, which represents the final selling price of the property, along with factors like YearBuilt, Neighborhood, TotalLivingArea, Acres, and Bedrooms that may influence the price. The dataset also includes categorical variables such as Style, Occupancy, and Neighborhood, as well as logical indicators like AC and FirePlace. By examining these variables together, we can better understand patterns in housing characteristics and how different factors may affect property values in Ames.

# Step 2 result

**Samara's thoughts:** I do agree with the rest that sales price would be the main variable. I think other variables of interest could be sale-date, occupancy, bedrooms, totalLivingArea, and Neighboorhood. This is because these values would be the most influential variables that control sale Price, along with any other variables the others mentioned.

**Wyatt's thoughts:** The main variable is sales price, which means that its the price of each property sold in Ames. Its important because it shows the values of homes and allows us to look at how the other variables effect it. 

**Tanisha's thoughts:** Yes. The main variable of interest is Sale Price, which represents the final price at which a home is sold. The other variables, such as Year Built, Acres, Neighborhood, and Total Living Area, may help explain or influence the sale price.

**(Combined) As a team, we found that** the main variable of interest in the dataset is Sale Price, since it represents the final price at which each property in Ames was sold. This variable is important because it reflects the value of homes and allows us to analyze how different property characteristics may influence that value. Other variables such as Sale Date, Occupancy, Bedrooms, TotalLivingArea, YearBuilt, Acres, and Neighborhood are also important because they can help explain differences in sale prices. By examining how these variables relate to Sale Price, we can better understand the factors that affect.

# Step 3 result

```{r}
summary(ames$`Sale Price`)
range(ames$`Sale Price`, na.rm = TRUE)
```

```{r}
library(ggplot2)

ggplot(ames, aes(x = `Sale Price`)) +
  geom_histogram(bins = 25, fill = "blue", color = "red") +
  labs(
    title = "Distribution of Sale Prices in Ames",
    x = "Sale Price",
    y = "Number of Homes"
  )
```

```{r}
# ggplot with the log of sale price
ggplot(ames, aes(x = log(`Sale Price`))) +
  geom_histogram(bins = 50, fill = "blue", color = "red") +
  labs(
    title = "Distribution of Sale Prices in Ames",
    x = "Sale Price",
    y = "Number of Homes"
  )
```

**Samara's thoughts:** The range of the variable "Sale Price" is between 0 to 20,500,000. There are a few outliers both on the high price and low price end, but the majority of the sale prices are around the meadian at 170900. The super high cost properties do increase the mean to 1017479.

**Wyatt's thoughts:** Houses range from 0 to 20500000 dollars with the median being 170900. The distribution of sale prices is highly right skewed. This means that most homes sell for moderate prices with a few outliers of very high price. There are properties with a sale price of 0, which probably means that the data was incorrectly recorded.

**Tanisha's thoughts:** The main variable is Sale Price. Home prices range from $0 to $20,500,000, with a median price of $170,900. The histogram shows the data is right-skewed, meaning most homes sell for moderate prices and only a few sell for very high prices. Although there are some outliers that have a price of $0 which I believe could be due to missing data.

**(Combined) As a team, we found that** the Sale Price variable ranges from $0 to $20,500,000, with a median value of about $170,900. The distribution of sale prices is right-skewed, meaning that most homes sell for moderate prices while a small number of homes sell for extremely high prices, creating high-value outliers that increase the mean. We also noticed that some properties have a sale price of $0, which likely indicates missing, incorrect, or special-case data rather than actual home sales. Overall, the data shows that most homes in Ames sell near the median price, with only a few very expensive properties affecting the overall distribution.

# Step 4 result

**Samara's work:**

I chose the number of bedrooms as my variable. The range of this variable is between 0 and 10, with the most common number of bedrooms at 3. There is also a fairly symmetric distribution around the mean at about 3.3.

Summary, range and plot of bedrooms:

```{r}
summary(ames$Bedrooms)
range(ames$Bedrooms, na.rm = TRUE)

ames |>
  ggplot(aes(x = factor(Bedrooms))) +
    geom_bar(fill='blue') +
      labs(title = "Distribution of bedrooms", x = "Number of bedrooms", y = "Count")
```

Plot of bedrooms vs sale price:

```{r}
ames |>
  ggplot(aes(x = factor(Bedrooms), y = log10(`Sale Price`))) +
    geom_boxplot(fill = 'blue') + labs(title = "Sale Price by Number of Bedrooms", x  = "Number of Bedrooms", y ="Log(Sale Price)")

```

Now, overall, the relationship between the Sale Price and number of bedrooms, is that the median of the Sale Price increases as the number of bedrooms increase. Now, something interesting is that when Number of Bedrooms = 1, there is a super large upper quartile, meaning that there are numerous 1 bedrooms that were sold at higher prices, which follows up on the oddity found.

---

**Wyatt's Plot:**

```{r}
summary(ames$`TotalLivingArea (sf)`)
range(ames$`TotalLivingArea (sf)`, na.rm = TRUE)


ggplot(ames, aes(x = `TotalLivingArea (sf)`)) +
  geom_histogram(bins = 25, fill = "blue", color = "red") +
  labs(
    title = "Distribution of Total Living Area",
    x = "Total Living Area",
    y = "Number of Homes"
  )
```

Wyatt's work: Total living Area measures the interior living space of the home. The histogram shows that fewer home have large living space. It is right skewed meaning that large homes are not common. The relationship between them is positive as when one increases they both increase. This is also seen in 3 with some of the outliers. However, some smaller homes can sell for higher, meaning that there are other factors as well. 

---

**Tanisha's Plot:**

```{r}
ames %>%
  filter(`Sale Price` > 0) %>%
  group_by(Neighborhood) %>%
  summarize(avg_price = mean(`Sale Price`, na.rm = TRUE)) %>%
  arrange(desc(avg_price)) %>%
  slice_head(n = 15) %>%
  ggplot(aes(x = avg_price, y = reorder(Neighborhood, avg_price))) +
  geom_col(fill = "steelblue") +
  scale_x_continuous(
    labels = scales::dollar,
    breaks = seq(100000, 12000000, by = 3000000)
  ) +
  labs(
    title = "Top 15 Neighborhoods by Average Sale Price",
    x = "Average Sale Price",
    y = "Neighborhood"
  ) +
  theme_minimal()
```

Tanisha's work: I chose the variable Neighborhood to examine how location relates to Sale Price. The bar chart shows the top 15 neighborhoods with the highest average sale prices. The results indicate that home prices vary across neighborhoods, suggesting that location influences property value. One neighborhood, Investor Owned, has a much higher average price than the others, likely due to a few very high-priced sales influencing the overall data.

---
