---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(classdata)

data(ames, package = "classdata")
```

# Lab report #1

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

# Step 1 result
```{r}
ames |> slice_head(n = 6)
dim(ames)
```
```{r}
glimpse(ames)
```

Samara's thoughts:

Wyatt's thoughts: The data set contains 6935 rows and 16 columns, where rows represent a residential property sale. Key variables include year built, acres, neighborhood, and TotalLivingArea. The main variable is Sale Price which represents the final sale price of the home. Depending on the variables listed above cna chang the range of the variables.

(Name) thoughts:

(Name) thoughts:

(Combined) As a team, we found that ...

# Step 2 result
Samara's thoughts:

Wyatt's thoughts:

(Name) thoughts:

(Name) thoughts:

(Combined) As a team, we found that ...

# Step 3 result
Samara's thoughts:

Wyatt's thoughts:

(Name) thoughts:

(Name) thoughts:

(Combined) As a team, we found that ...

# Step 4 result
Samara's work:

(Name) work:

(Name) work:

(Name) work:
